Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.Rmd
figure heights - correlation between resource and challenge now .95 (what happened)?

```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance."}

@@

```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales)."}

>>>>

```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.", fig.height=10}

@@

```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales).", fig.height=10}
